---
title: "plots_caroline_final"
author: "Caroline Wendt"
date: "12/9/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.path = "../figs/", echo = TRUE,
                      error = FALSE, message = FALSE, warning = FALSE)
```

# Packages
```{r}
# packages for data filtering
library(readr)
library(dplyr)
library(stringr)
library(fuzzyjoin)

# packages for plots
library(ggplot2)
library(viridis)
library(forcats)
library(plotly)
library(ggthemes)
```

______________________________________________________________________________

# Filtering
## filter data by subject using Eric's script for AP subject joining
### see `subject_filtering_and_joining.Rmd`

```{r}
jeop_data <- read_tsv(file = "../data/jeopardy_clue_dataset-master/master_season1-35.tsv")

bio_data <- readr::read_csv(file = "../data/ap_biology.csv", 
                            col_names = FALSE) %>% 
  dplyr::rename(vocab_term = X1) %>% 
  dplyr::mutate(subject = "biology") %>% 
  dplyr::select(subject, dplyr::everything())
```

```{r}
ap_subjects <- c("biology", "chemistry", "physics", "history", "liturature")

school_jeop <- jeop_data %>% 
  dplyr::arrange(category) %>% 
  dplyr::mutate(category = stringr::str_to_lower(category)) %>% 
  dplyr::filter(category %in% ap_subjects)
``` 

```{r}
# join AP bio data with jeopardy data
joined_data <- fuzzyjoin::regex_inner_join(x = school_jeop, 
                                           y = bio_data, 
                                           by = c("question" = "vocab_term"))
```

Below is a function to match the "question" from the jeopardy dataframe to the corresponding key term in a subject data frame. The function expects the standard jeopardy dataframe as well as a key terms dataframe for a given subject. There should be a subject column with the subject (e.g., "science") listed for each row next to each vocab term. This column is what will later be used to group the jeopardy questions by subject. I use `regex_inner_join` to perform robust, inexact matching on the jeopardy questions. This approach nearly doubles the number of matches without including irrelevant matches.

```{r}
join_by_subject <- function(jeop_df, subject_df) {
  # Make question column lower case
  jeop_df <- jeop_df %>% 
    dplyr::mutate(question = stringr::str_to_lower(question))
  
  subject_df <- subject_df %>% 
    dplyr::mutate(vocab_term = stringr::str_to_lower(vocab_term))
  
  joined_df <- fuzzyjoin::regex_inner_join(x = jeop_df,
                                           y = subject_df,
                                           by = c("question"= "vocab_term"))
  return(joined_df)
}
```

Below is a call to the join function in order to test it.
```{r}
join_test <- join_by_subject(school_jeop, bio_data)
```

_______________________________________________________________________________

# Plots 1-3
## Heat maps

Background info (Jeopardy show structure)
- round 1: 200 400 600 800 1000 (different for older years)
- round 2: 400 800 1200 1600 2000 (different for older years)
- round 3: wagers /final jeopardy (don't use)
- extra: daily doubles (round 1 and 2; separate plot)

first: exclude daily doubles for each round (people wager more if it is an easier subject)

### Round 1
```{r}
# data for round 1
heat_data_r1 <- join_test %>%
  dplyr::filter(daily_double %in% "no",
                round == 1) %>% 
  dplyr::select(round, value, subject) %>%
  dplyr::mutate_at(vars(round, value, subject), funs(factor(.))) %>% 
  dplyr::group_by(round, value, subject) %>%
  count() %>%
  ungroup()

heat_data_r1 %>% 
  slice(1:5)
```

```{r}
# interactive version of heat map for round 1
hmap_1_interact <- ggplot(heat_data_r1,
                          aes(x = subject, y = value)) +
  geom_tile(aes(fill = n)) +
  scale_fill_viridis(option = "viridis", direction = -1) +
  labs(x = "Subject", y = "Value", 
       fill = "Number of \noccurences",
       title = "Round 1: Number of occurences of subject by value") +
  theme_light()
  
ggplotly(hmap_1_interact)
```


### Round 2
```{r}
# data for round 2
heat_data_r2 <- join_test %>%
  dplyr::filter(daily_double %in% "no",
                round == 2) %>% 
  dplyr::select(round, value, subject) %>%
  dplyr::mutate_at(vars(round, value, subject), funs(factor(.))) %>% 
  dplyr::group_by(round, value, subject) %>%
  count() %>%
  ungroup()

heat_data_r2 %>% 
  slice(1:5)
```

```{r}
# interactive version of heat map for round 2
hmap_2_interact <- ggplot(heat_data_r2, 
                          aes(x = subject, y = value)) +
  geom_tile(aes(fill = n)) +
  scale_fill_viridis(option = "magma", direction = -1) +
  labs(x = "Subject", y = "Value", 
       fill = "Number of \noccurences",
       title = "Round 2: Number of occurences of subject by value") +
  theme_light()
  
ggplotly(hmap_2_interact)
```

### Daily Doubles
```{r}
# data for daily doubles
heat_data_dd <- join_test %>%
  dplyr::filter(daily_double %in% "yes") %>% 
  dplyr::select(daily_double, value, subject) %>%
  dplyr::mutate_at(vars(daily_double, value, subject), funs(factor(.))) %>% 
  dplyr::group_by(daily_double, value, subject) %>%
  count() %>%
  ungroup()

heat_data_dd %>% 
  slice(1:5)
```

```{r}
# interactive version of heat map for daily doubles
hmap_dd_interact <- ggplot(heat_data_dd, 
                          aes(x = subject, y = value)) +
  geom_tile(aes(fill = n)) +
  scale_fill_viridis(option = "plasma", direction = -1) +
  labs(x = "Subject", y = "Value", 
       fill = "Number of \noccurences",
       title = "Daily Doubles: Number of occurences of subject by value") +
  theme_light()
  
ggplotly(hmap_dd_interact)
```


