---
title: "AP Subject Joining"
author: "Eric Wendt"
date: "12/4/2019"
output: pdf_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readr)
library(dplyr)
library(stringr)
library(fuzzyjoin)
```

```{r message=FALSE, warning=FALSE}
jeop_data <- readr::read_tsv(file = "data/jeopardy_clue_dataset-master/master_season1-35.tsv")
bio_data <- readr::read_csv(file = "data/ap_biology.csv", col_names = FALSE) %>% 
  dplyr::rename(vocab_term = X1) %>% 
  dplyr::mutate(subject = "biology") %>% 
  dplyr::select(subject, dplyr::everything())
```

```{r}
ap_subjects <- c("biology", "chemistry", "physics", "history", "liturature")

school_jeop <- jeop_data %>% 
  dplyr::arrange(category) %>% 
  dplyr::mutate(category = stringr::str_to_lower(category)) %>% 
  dplyr::filter(category %in% ap_subjects)
``` 

```{r}
joined_data <- fuzzyjoin::regex_inner_join(x = school_jeop, y = bio_data, by = c("question"= "vocab_term"))
```

Below is a function to match the question from the jeopardy data frame to the corresponding key term in a subject data frame. The function expects the standard jeopardy dataframe as well as a key terms data frame for a given subject. There should be a subject column with the subject (i.e. "science") listed for each row next to each vocab term. This column is what will later be used to group the jeopardy questions by subject. I use regex_inner_join to perform robust, inexact matching on the jeopardy questions. This approach nearly double the number of matches without including irrelevant matches.

```{r}
join_by_subject <- function(jeop_df, subject_df) {
  # Make question column lower case
  jeop_df <- jeop_df %>% 
    dplyr::mutate(question = stringr::str_to_lower(question))
  
  subject_df <- subject_df %>% 
    dplyr::mutate(vocab_term = stringr::str_to_lower(vocab_term))
  
  joined_df <- fuzzyjoin::regex_inner_join(x = jeop_df, y = subject_df, by = c("question"= "vocab_term"))
  return(joined_df)
}
```

Below is a call to the join function in order to test it.

```{r}
join_test <- join_by_subject(school_jeop, bio_data)
```





